---
title: "Catchment based Assessment for BEGA EMU"
output: html_document
classoption:
- twocolumn
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

load('CHR_test_run.RData')

```

\
\
\

:::::::::::::: {.columns}
::: {.column width="50%"}

## ** Harvestable Rights - Catchment based assessment: BEGA River Catchment EMU Summary **
```{r fig.width = 15, fig.height = 8}

EMU_plot <- 
    
    tm_shape(NSW_CHR_Water_Sources_aggregated_test) +
    tm_polygons(col = "tan1") +
    # tm_borders("black", lwd = 1) +
    
    tm_shape(EMU_dam_feat) +
    tm_polygons(col = "lightblue") +
    # tm_raster("elevation", palette = terrain.colors(10)) +
    
    tm_shape(EMU_Stream_Order) +
    tm_lines(col="blue", lwd="STRAHLER", scale=2, legend.lwd.show = FALSE) +
    
    tm_scale_bar(breaks = c(0, 10, 20), text.size = 1,
                 position=c("left", "bottom")) +
    tm_compass(type = "arrow", size = 2, position = c("left", "top")) +
    tm_layout(legend.outside = TRUE) +
    tm_legend(position = c("left", "bottom"), bg.color = "grey95", frame = TRUE)


EMU_plot

```

\
\
\

## ** EMU Characteristics Snapshot (formatting and shortlist of variable tbd) **

```{r}

## Water source table of key variables 1).
EMU_summary_tibble


```


:::::::::::::: {.columns}
::: {.column width="40%"}


## ** Harvestable Rights Limit Options – impact by theme  (can incl CC) **
```{r fig.width = 20, fig.height = 12}

plot_grid(EMU_theme_20, EMU_theme_30,
          EMU_theme_40, EMU_theme_50, ncol = 2)


```

\
\
\

## ** Summary of hydrology change across all gauges  (can incl CC) **

```{r}

## View here
EMU_flow_flex

```


\newpage


## ** Harvestable Rights - Catchment based assessment: Bega River Catchment EMU Summary **

```{r}

CHR_DC_EMU_master_flex

```


\newpage


:::::::::::::: {.columns}
::: {.column width="30%"}


## ** Harvestable Rights - Catchment based assessment: Bega River Estuary and Tributaries WS1 **
```{r fig.width = 10, fig.height = 5}

EMU_plot

```


## ** Water Source 1: Characteristics Snapshot **

```{r}

## Water source table of key variables 1).
WS_summary_tibble


```



## ** Water Source 1: Flow Duration Curve Changes (Each Scenario) **
```{r fig.width = 10, fig.height = 5}

fdc.10pc = fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn`,    new = TRUE,  ylab = "Q ft3/s", cex = 0.8)
fdc.30pc =fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn_30%`, new = FALSE, col  = "red",     cex = 0.8)
fdc.50pc =fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn_50%`, new = FALSE, col  = "blue",    cex = 0.8)
legend("topright", c("10%", "30%", "50%"), col = c("black","red","blue"), lty = c(1,1,1))

```


:::::::::::::: {.columns}
::: {.column width ="70%"}

<!-- ## ** Water Source 1: Risk Per Decision Criteria ** -->
```{r fig.width = 20, fig.height = 8}

WS1_DC_10

```


```{r fig.width = 20, fig.height = 8}

WS1_DC_50

```




\newpage


:::::::::::::: {.columns}
::: {.column width="30%"}


## ** Harvestable Rights - Catchment based assessment: Mid Bega River Tributaries WS2 **
```{r fig.width = 10, fig.height = 5}

EMU_plot

```


## ** Water Source 2: Characteristics Snapshot **

```{r}

## Water source table of key variables 1).
WS_summary_tibble 


```



## ** Water Source 2: Flow Duration Curve Changes (Each Option) **
```{r fig.width = 10, fig.height = 5}

fdc.10pc = fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn`,     new = TRUE,  ylab = "Q ft3/s", cex = 0.8)
fdc.20pc = fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn_30%`, new = FALSE, col  = "red",     cex = 0.8)
fdc.30pc = fdc(baseline_ws_gauges_combined$`BEGA_219001_Rutherford Brown Mtn_50%`, new = FALSE, col  = "blue",    cex = 0.8)
legend("topright", c("10%", "30%", "50%"), col = c("black","red","blue"), lty = c(1,1,1))

```


:::::::::::::: {.columns}
::: {.column width ="50%"}

## ** Water Source 2: Risk Per Decision Criteria **
```{r fig.width = 20, fig.height = 8}

WS2_DC_10

```

```{r fig.width = 20, fig.height = 8}

WS2_DC_50

```


\newpage


\newpage

## ** Harvestable Rights - Catchment based assessment: BEGA River Catchment EMU Summary Maps (10%) **
```{r fig.width = 25, fig.height = 15}

## Create a panel of tmaps
tmap_arrange(DC_1.2_10_pc,
             DC_1.3_10_pc,
             DC_1.4_10_pc,
             DC_1.7_10_pc,
             ncol = 2,
             nrow = 2)


```

\newpage


## ** Harvestable Rights - Catchment based assessment: BEGA River Catchment EMU Summary Maps (30%) **
```{r fig.width = 25, fig.height = 15}

tmap_arrange(DC_1.2_10_pc,
             DC_1.3_10_pc,
             DC_1.4_10_pc,
             DC_1.7_10_pc,
             ncol = 2,
             nrow = 2)

```

\newpage


## ** Harvestable Rights - Catchment based assessment: BEGA River Catchment EMU Summary Maps (50%) **
```{r fig.width = 40, fig.height = 12}

tmap_arrange(DC_1.2_10_pc,
             DC_1.3_10_pc,
             DC_1.4_10_pc,
             DC_1.7_10_pc,
             ncol = 2,
             nrow = 2)

```


